---
title: "Homework3: Hotel Booking Dataset "
description: | This Weigeng's Homework 3
author: WeigengLi
date: 08-16-2021
output:
  distill::distill_article:
    self_contained: false
draft: true
---

The data set was about Booking Information of hotels.
First Let's have a quick glimpse of the data set


# read and take a glimpse of data

```{r, echo=FALSE}
knitr::opts_chunk$set(echo = FALSE)
library("tidyverse")
library(dplyr)
HBD<-read_csv("../../_data/hotel_bookings.csv")
head(HBD)
```


I found that some column is no easy to read. So I made some changes.
The 2<sup>nd</sup> column "is_canceled" is contained in 31<sup>th</sup> "reservation_status". We can combine 2 columns into 1 column State.

```{r}
colum2_colum31<- HBD %>% select(is_canceled,reservation_status) %>% slice(121:129)
head(colum2_colum31)
```

Codes

```{r,echo=TRUE}
HBD <- HBD %>%
  mutate( "State" = case_when(
          is_canceled == 1 & reservation_status == 'Canceled'  ~ "Canceled" ,
          is_canceled == 0 & reservation_status == 'Check-Out' ~ "Check-Out",
          is_canceled == 1 & reservation_status == 'No-Show'   ~ "Canceled" ,
         )
         )
colum_State<- HBD %>% select(State)%>% slice(121:129)
head(colum_State)
```

After Combination

```{r,echo=FALSE}
head(colum_State)
```

Using group_by() and summarise() we can find out that individuals who canceled the order have more leading time. 

```{r}
HBDState<- HBD %>%
  group_by(State)
summarise(HBDState, mean(lead_time))

```
To compare number of orders in each market segments. I use a bar graph.

```{r}
HBD3<- HBD%>%
  select(hotel,country,market_segment,lead_time)
ggplot(HBD3,aes(hotel,fill=market_segment))+
  geom_bar()

```

Notice that there was some undefined group use filter to delete it

```{r}
HBD3<- HBD%>%
  filter(!str_detect(market_segment,"Undefined"))%>%
  select(hotel,country,market_segment,lead_time)
ggplot(HBD3,aes(hotel,fill=market_segment))+
  geom_bar()

```






